\( \tool \): JavaScript IR-based Semantics Extraction Toolchain

### 2020-04-01 ase20/compiler.tex
[ASE] Revised about the word: ECMAScript

\item \textbf{Abstract data types:} \( \ires \) supports only three
abstract data types: \( \code{Record} \) for mappings from some values
to other values, \( \code{List} \) for sequential data, and
\( \code{Singleton} \) for singleton data.  For example, ECMAScript
environment records are represented as \( \code{Record} \)
from string values into addresses that represent other types of
\( \code{Record} \) for bindings.  We also represent constants
in the ECMAScript specification such as \( \code{empty} \)
and \( \code{normal} \) as \( \code{Singleton} \) data types
in \( \ires \).
\end{itemize}

>>>>

\item \textbf{Abstract data types:} \( \ires \) supports only three
abstract data types: \( \code{Record} \) for mappings from some values
to other values, \( \code{List} \) for sequential data, and
\( \code{Singleton} \) for singleton data.  For example, ECMAScript
environment records are represented as \( \code{Record} \)
from string values into addresses that represent other types of
\( \code{Record} \) for bindings.  We also represent constants
in ECMAScript such as \( \code{empty} \)
and \( \code{normal} \) as \( \code{Singleton} \) data types
in \( \ires \).
\end{itemize}

### 2020-04-01 ase20/conclusion.tex
[ASE] Revised about the word: ECMAScript

\section{Conclusion}\label{sec:conclude}
The annual updates of the ECMAScript specification makes it difficult to
build program analysis or formal verification of JavaScript due to the
required human efforts in modeling a moving target.  In this paper,
we proposed a tool \( \tool \), which \textit{automatically} extracts the
syntax and semantics specified in the ECMAScript specification.  The tool
generates a parser from a language grammar written in \( \bnfes \), and
compiles abstract algorithms written in English to \( \ires \) functions.
The only parts that require manual efforts are compile rules and
language-specific global setting, which we provide for ECMAScript
as an example case study.  We also support \textsf{Fault Localizer} to
adapt updates of the ECMAScript specification by suggesting new rules.
We evaluated \( \tool \) by applying it to ECMAScript 2020 with Test262.
The extracted semantics passed 19,220 of 19,282 applicable tests in Test262.
The tool also detected three confirmed errors from the specification.
Moreover, we showed that the tool is also applicable to an incomplete
language proposal. The implementation of the tool is publicly available
as an open-source project.

>>>>

\section{Conclusion}\label{sec:conclude}
The annual updates of the ECMAScript makes it difficult to
build program analysis or formal verification of JavaScript due to the
required human efforts in modeling a moving target.  In this paper,
we proposed a tool \( \tool \), which \textit{automatically} extracts the
syntax and semantics specified in ECMAScript.  The tool
generates a parser from a language grammar written in \( \bnfes \), and
compiles abstract algorithms written in English to \( \ires \) functions.
The only parts that require manual efforts are compile rules and
language-specific global setting, which we provide for ECMAScript
as an example case study.  We also support \textsf{Fault Localizer} to
adapt updates of ECMAScript by suggesting new rules.
We evaluated \( \tool \) by applying it to ES10 with Test262.
The extracted semantics passed 19,220 of 19,282 applicable tests in Test262.
The tool also detected three confirmed errors from the specification.
Moreover, we showed that the tool is also applicable to an incomplete
language proposal. The implementation of the tool is publicly available
as an open-source project.

### 2020-04-01 ase20/eval.tex
[ASE] Revised about the word: ECMAScript

We evaluate \( \tool \) based on the following four research questions:
\begin{itemize}[leftmargin=0.5cm]
\item RQ1. \textbf{Effectiveness:} Does \( \tool \) effectively reduce
manual efforts in extracting the syntax and semantics from existing
ECMAScript specifications? 
\item RQ2. \textbf{Correctness:} Do the extracted syntax and semantics
from ECMAScript 2020 behave correctly?
\item RQ3. \textbf{Adaptability:} Is \( \tool \) applicable to
incomplete feature proposals?
\item RQ4. \textbf{Usefulness:} Does \( \tool \) detect any
specification errors?
\end{itemize}

@@

We evaluate the effectiveness of \( \tool \) by applying it to the
most recent five versions of the ECMAScript specifications, ECMAScript
2016 to 2020.  We measured for how many grammar productions and
steps in abstract algorithms \( \tool \) automatically generates parsers and
semantics, respectively, in two respects: 1) in each version and 2) in
each difference between adjacent versions.

@@

\subsection{Correctness}
\begin{table}[t]
  \centering
  \caption{Testing results of Test262 for ECMAScript 2020}
  \label{table:test262}
\vspace*{-.5em}
\footnotesize
  \begin{tabular}{lr}\toprule
    \belowrulesepcolor{gainsboro}
    \rowcolor{gainsboro} \textbf{All Test262 Tests} & \textbf{36,794}\\
    \aboverulesepcolor{gainsboro}\midrule
    Annexes/Internationalization & 1,774\\\hdashline
    In-progress features & 5,895\\\midrule
    \belowrulesepcolor{gainsboro}
    \rowcolor{gainsboro} \textbf{ECMAScript 2020 Tests} & \textbf{29,125}\\
    \aboverulesepcolor{gainsboro}\midrule
    Non-strict mode tests & 1,136\\\hdashline
    Module tests& 918 \\\hdashline
    Early error tests & 1,316\\\hdashline
    Inessential built-in object tests & 6,473\\\midrule
    \belowrulesepcolor{gainsboro}
    \rowcolor{gainsboro} \textbf{Applicable Tests} & \textbf{19,282}\\
    \aboverulesepcolor{gainsboro}\midrule
    Passed tests & 19,220 \\\hdashline
    Failed tests & 62 \\\bottomrule
  \end{tabular}
\vspace*{-1em}
\end{table}

To evaluate the correctness of \( \tool \), we developed a JavaScript
interpreter based on the extracted syntax and semantics from
ECMAScript 2020.  Among 9,657 steps in ECMAScript 2020,
8,926 steps are automatically compiled via \textsf{Algorithm Compiler}.
Among the remaining 731 steps, we selected 381 steps
that are essential to the core semantics and manually
implemented their corresponding \( \ires \) functions
via the \textsf{Fault Localizer} introduced in Section~\ref{sec:localizer}.
Moreover, we implement the \textsf{Global Setting} except
the excluded language features discussed in Section~\ref{sec:exclusion}.

We tested the interpreter using Test262, the official conformance test
suite provided by TC39, as of August 6, 2019.  Because Test262
contains tests for extensions and in-progress features, we excluded
them to focus on the semantics of ECMAScript 2020.  As Table~\ref{table:test262} shows,
Test262 consists of 36,794 tests and we excluded 7,669 tests for
extensions and in-progress features.  We also filtered out
tests for excluded features described in Section~\ref{sec:impl}.
Finally, we tested 19,282 applicable tests and only 62 tests failed.
Among them, 54 tests utilize implementation-dependent features,
three are timeout with 20 minutes due to enormous computation,
and five are wrong tests.  Thus, we believe that all the
semantics extracted from \( \tool \) are correct.

@@

\subsection{Adaptability}
We show the adaptability of \( \tool \) with one case study: applying
it to an incomplete feature proposal.  Because ECMAScript is an open
standard language, various proposals are available with their own
specification changes and tests.  A
separate repository~\cite{proposals} maintains such proposals with six
different stages: Stage 0 to Stage 3, Finished, and Inactive.  Each
proposal starts with Stage 0, and the TC39 committee regularly
examines Stage 3 proposals to decide their next stages.  If a proposal
is confirmed, the committee changes its stage to Finished and
integrates it into the next version of the ECMAScript specification.
Otherwise, the committee changes its stage to Inactive.  Thus, we
applied \( \tool \) to one Stage 3 proposal.
%https://github.com/tc39/proposal-optional-chaining

The optional chaining operator (\( \code{?.} \)) is one of Stage 3
proposals that removes specific boilerplate code.  It detects a code
pattern like \( \code{x \&\& x.p} \), which first checks that the
value of \( \code{x} \) is not \( \code{undefined} \) and then
accesses its property \( \code{p} \).  With the optional chaining
operator, we can reduce code size by implementing it as \( \code{x?.p} \).
We extended ECMAScript 2020 with this proposal and applied \( \tool \)
to the extended specification.  We found that \textsf{Parser Generator}
successfully handled three updated lexical productions and three
updated syntactic productions.  For semantics, the proposal had 22
updated abstract algorithms.  At the first attempt,
\textsf{Algorithm Compiler} succeeded compiling only 10 algorithms.
However, we noticed that several algorithm steps have different styles
from existing ECMAScript specifications.  Thus, we revised them to the
original style, sent three pull requests to the GitHub repository
of the proposal, and the authors of the proposal accepted our pull
requests\footnote{The URL of three pull requests are anonymized 
due to a double-blind review process.}.  After revision, 21 of 22
algorithms are successfully compiled and we manually compiled only one
algorithm.  Test262 has 33 tests for the optional chaining operator
and six of them are semantics tests.  The semantics extracted with the
optional chaining operator proposal successfully passed all the six
semantics tests.  This case study shows that \( \tool \) is applicable
to future language features and it could be useful as a specification
writing guide.

\subsection{Usefulness}
We show the usefulness of \( \tool \) with one case study:
specification error detection.  While applying \( \tool \) to
ECMAScript 2020, we found three specification errors.  We fixed them
and sent pull requests to the official GitHub repository of
ECMAScript~\cite{es2020}.  They were all confirmed by TC39
and will be fixed in the next release \footnote{The URL of three pull
requests are anonymized due to a double-blind review process.}.

>>>>

We evaluate \( \tool \) based on the following four research questions:
\begin{itemize}[leftmargin=0.5cm]
\item RQ1. \textbf{Effectiveness:} Does \( \tool \) effectively reduce
manual efforts in extracting the syntax and semantics from existing
ECMAScript specifications? 
\item RQ2. \textbf{Correctness:} Do the extracted syntax and semantics
from ES10 behave correctly?
\item RQ3. \textbf{Adaptability:} Is \( \tool \) applicable to
incomplete feature proposals?
\item RQ4. \textbf{Usefulness:} Does \( \tool \) detect any
specification errors?
\end{itemize}

@@

We evaluate the effectiveness of \( \tool \) by applying it to the
most recent five versions of ECMAScript, ES6 to ES10.
We measured for how many grammar productions and
steps in abstract algorithms \( \tool \) automatically generates parsers and
semantics, respectively, in two respects: 1) in each version and 2) in
each difference between adjacent versions.

@@

\subsection{Correctness}
\begin{table}[t]
  \centering
  \caption{Testing results of Test262 for ES10}
  \label{table:test262}
\vspace*{-.5em}
\footnotesize
  \begin{tabular}{lr}\toprule
    \belowrulesepcolor{gainsboro}
    \rowcolor{gainsboro} \textbf{All Test262 Tests} & \textbf{36,794}\\
    \aboverulesepcolor{gainsboro}\midrule
    Annexes/Internationalization & 1,774\\\hdashline
    In-progress features & 5,895\\\midrule
    \belowrulesepcolor{gainsboro}
    \rowcolor{gainsboro} \textbf{ES10 Tests} & \textbf{29,125}\\
    \aboverulesepcolor{gainsboro}\midrule
    Non-strict mode tests & 1,136\\\hdashline
    Module tests& 918 \\\hdashline
    Early error tests & 1,316\\\hdashline
    Inessential built-in object tests & 6,473\\\midrule
    \belowrulesepcolor{gainsboro}
    \rowcolor{gainsboro} \textbf{Applicable Tests} & \textbf{19,282}\\
    \aboverulesepcolor{gainsboro}\midrule
    Passed tests & 19,220 \\\hdashline
    Failed tests & 62 \\\bottomrule
  \end{tabular}
\vspace*{-1em}
\end{table}

To evaluate the correctness of \( \tool \), we developed a JavaScript
interpreter based on the extracted syntax and semantics from ES10.
Among 9,657 steps in ES10,
8,926 steps are automatically compiled via \textsf{Algorithm Compiler}.
Among the remaining 731 steps, we selected 381 steps
that are essential to the core semantics and manually
implemented their corresponding \( \ires \) functions
via the \textsf{Fault Localizer} introduced in Section~\ref{sec:localizer}.
Moreover, we implement the \textsf{Global Setting} except
the excluded language features discussed in Section~\ref{sec:exclusion}.

We tested the interpreter using Test262, the official conformance test
suite provided by TC39, as of August 6, 2019.  Because Test262
contains tests for extensions and in-progress features, we excluded
them to focus on the semantics of ES10.  As Table~\ref{table:test262} shows,
Test262 consists of 36,794 tests and we excluded 7,669 tests for
extensions and in-progress features.  We also filtered out
tests for excluded features described in Section~\ref{sec:impl}.
Finally, we tested 19,282 applicable tests and only 62 tests failed.
Among them, 54 tests utilize implementation-dependent features,
three are timeout with 20 minutes due to enormous computation,
and five are wrong tests.  Thus, we believe that all the
semantics extracted from \( \tool \) are correct.

@@

\subsection{Adaptability}
We show the adaptability of \( \tool \) with one case study: applying
it to an incomplete feature proposal.  Because ECMAScript is an open
standard language, various proposals are available with their own
specification changes and tests.  A
separate repository~\cite{proposals} maintains such proposals with six
different stages: Stage 0 to Stage 3, Finished, and Inactive.  Each
proposal starts with Stage 0, and the TC39 committee regularly
examines Stage 3 proposals to decide their next stages.  If a proposal
is confirmed, the committee changes its stage to Finished and
integrates it into the next version of ECMAScript.
Otherwise, the committee changes its stage to Inactive.  Thus, we
applied \( \tool \) to one Stage 3 proposal.
%https://github.com/tc39/proposal-optional-chaining

The optional chaining operator (\( \code{?.} \)) is one of Stage 3
proposals that removes specific boilerplate code.  It detects a code
pattern like \( \code{x \&\& x.p} \), which first checks that the
value of \( \code{x} \) is not \( \code{undefined} \) and then
accesses its property \( \code{p} \).  With the optional chaining
operator, we can reduce code size by implementing it as \( \code{x?.p} \).
We extended ES10 with this proposal and applied \( \tool \)
to the extended specification.  We found that \textsf{Parser Generator}
successfully handled three updated lexical productions and three
updated syntactic productions.  For semantics, the proposal had 22
updated abstract algorithms.  At the first attempt,
\textsf{Algorithm Compiler} succeeded compiling only 10 algorithms.
However, we noticed that several algorithm steps have different styles
from existing ECMAScript.  Thus, we revised them to the
original style, sent three pull requests to the GitHub repository
of the proposal, and the authors of the proposal accepted our pull
requests\footnote{The URL of three pull requests are anonymized 
due to a double-blind review process.}.  After revision, 21 of 22
algorithms are successfully compiled and we manually compiled only one
algorithm.  Test262 has 33 tests for the optional chaining operator
and six of them are semantics tests.  The semantics extracted with the
optional chaining operator proposal successfully passed all the six
semantics tests.  This case study shows that \( \tool \) is applicable
to future language features and it could be useful as a specification
writing guide.

\subsection{Usefulness}
We show the usefulness of \( \tool \) with one case study:
specification error detection.  While applying \( \tool \) to
ES10, we found three specification errors.  We fixed them
and sent pull requests to the official GitHub repository of
ECMAScript~\cite{es2020}.  They were all confirmed by TC39
and will be fixed in the next release \footnote{The URL of three pull
requests are anonymized due to a double-blind review process.}.

### 2020-04-01 ase20/impl.tex
IEEETran format for ASE'20
[ASE] Revised about the word: ECMAScript

\section{Implementation}\label{sec:impl}
We describe the implementation detail of our open-source
tool, \( \tool \)\footnote{The URL of the tool is anonymized due to a
double-blind review process.}, which targets
ECMAScript 2020~\cite{es2020}.

%We describe how we implement an open-source \( \tool \)\footnote{
%The URL of the tool is anonymized due to a double-blind review process.},
%which targets ECMAScript 2020~\cite{es2020}.

\subsection{Excluded Language Features}\label{sec:exclusion}
We decided not to support the following ECMAScript 2020 features:

\vspace*{-.5em}
\paragraph{Non-Strict Mode}
Since ECMAScript 5, JavaScript introduced strict mode to
provide different semantics.  It
provides more stable semantics by preventing unsafe actions or
throwing originally ignored errors.  However, the ECMAScript
specification states that ``Strict mode does not restrict or modify
any aspect of the ECMAScript semantics that must operate consistently
across multiple source text units.''  Thus, we decided to support only
strict mode.

@@

\vspace*{-.5em}
\paragraph{Early Errors}
ECMAScript specifications use Early Error Rules to preclude invalid code
before evaluation. For example, an Early Error Rule checks whether
functions have duplicated parameters in strict mode.
Because they are written in different styles from abstract algorithms,
we do not support Early Error Rules.

@@

\subsection{Compile Rules for ECMAScript}
\begin{table}[t]
  \centering
  \caption{Compile rules in ECMAScript 2020}
  \label{table:rules}
\vspace*{-1em}
  \[
    \begin{array}{c?r|r|r|r|r|r|r}
      \text{Name}
      & \multicolumn{1}{c|}{\code{Stmt}}
      & \multicolumn{1}{c|}{\code{Expr}}
      & \multicolumn{1}{c|}{\code{Cond}}
      & \multicolumn{1}{c|}{\code{Value}}
      & \multicolumn{1}{c|}{\code{Ty}}
      & \multicolumn{1}{c|}{\code{Ref}}
      & \multicolumn{1}{c}{\code{SecNo}}\\\hline
      \text{\# Rules}
      & 17
      & 16
      & 8
      & 11
      & 33
      & 7
      & 21
    \end{array}
  \]
\vspace*{-2em}
\end{table}

As we discussed in Section~\ref{sec:compiler}, \textsf{Algorithm Compiler}
requires compile rules to compile given abstract algorithms to \( \ires \)
functions.  In order to cover the entire ECMAScript 2020 specification,
we defined compile rules for only seven kinds as summarized in
Table~\ref{table:rules}.  The compile rule for statements, \( \code{Stmt} \),
contains 17 compile rules and generates \( \ires \) instructions.
The \( \code{Expr} \), \( \code{Cond} \), and \( \code{Value} \) compile
rules denote expressions, conditions, and values, respectively.  While
all of them generate \( \ires \) expressions, they represent different
contexts in the ECMAScript specification.  For example,
\( \code{Expr} \) represents a context where any expression can appear,
\( \code{Cond} \) denotes a context where any boolean-valued expression
can appear, and \( \code{Value} \) represents a context where a fully
evaluated value can appear.  The \( \code{Ty} \) compile rule denotes
type names and generates string primitives in \( \ires \).  The \( \code{Ref} \)
represents references such as identifier lookup and member accesses of
map-like structures.  It generates \( \ires \) reference expressions.
Finally, the \( \code{SecNo} \) compile rule denotes section numbers
like \( \code{9.5.12} \), and it converts such numbers to
corresponding name strings like \( \code{"ProxyExoticObject.Call"} \).
% \begin{lstlisting}[style=myScalastyle]
% lazy val SecNo =
%   "9.5.12" ^^ { case x => "ProxyExoticObject.Call" } |||
%   ...
% \end{lstlisting}

\subsection{Global Setting}
We manually implemented \textsf{Global Setting} for ECMAScript 2020,
which has two parts: ECMAScript data types and built-in objects.

\vspace*{-.5em}
\paragraph{ECMAScript Data Types}
In ECMAScript 2020, Section 6 \textsf{ECMAScript Data Types and Values}
describes data types used in the specification.  It describes not only
data types explicitly exposed for JavaScript evaluation, but also all
the internal data types used in the specification.  For example, the
Environment Records are record types from identifiers to bindings for
values.  They are not explicitly accessible in JavaScript programs
but defined and used internally in the specification.

Each ECMAScript data type has several fields to store their relevant values.
We should implement such structures in order to correctly evaluate JavaScript
programs, but fields of ECMAScript data types could be abstract algorithms.
We call them \textit{method-like abstract algorithms} because they
implicitly get their receiver objects as arguments at callsites.
To mimic such implicit behaviors, we added a special variable
\( \code{this} \) as the first parameter of a method-like abstract algorithm,
and passed a receiver object at its callsite by modifying
\textsf{Algorithm Compiler}.  For example, an Environment Record has
the \textsf{DeleteBinding (N)} abstract algorithm as one of its fields.
Then, it gets two parameters, the special parameter \( \code{this} \)
and normal one \( \code{N} \).  Thus, the following algorithm step:
\begin{center}
  \includegraphics[width=0.2\textwidth]{img/method-like-example.png}
\end{center}
is compiled into the following \( \ires \) instruction:
\begin{lstlisting}[style=ires]
return DclRec.DeleteBinding(DclRec, N)
\end{lstlisting}

>>>>

\section{Implementation}\label{sec:impl}
We describe the implementation detail of our open-source
tool, \( \tool \)\footnote{The URL of the tool is anonymized due to a
double-blind review process.}, which targets ES10~\cite{es10}.

%We describe how we implement an open-source \( \tool \)\footnote{
%The URL of the tool is anonymized due to a double-blind review process.},
%which targets ES10~\cite{es10}.

\subsection{Excluded Language Features}\label{sec:exclusion}
We decided not to support the following ES10 features:

\vspace*{-.5em}
\paragraph{Non-Strict Mode}
Since ES5.1, JavaScript introduced strict mode to
provide different semantics.  It
provides more stable semantics by preventing unsafe actions or
throwing originally ignored errors.  However, ECMAScript
states that ``Strict mode does not restrict or modify
any aspect of the ECMAScript semantics that must operate consistently
across multiple source text units.''  Thus, we decided to support only
strict mode.

@@

\vspace*{-.5em}
\paragraph{Early Errors}
ECMAScript uses Early Error Rules to preclude invalid code
before evaluation. For example, an Early Error Rule checks whether
functions have duplicated parameters in strict mode.
Because they are written in different styles from abstract algorithms,
we do not support Early Error Rules.

@@

\subsection{Compile Rules for ECMAScript}
\begin{table}[t]
  \centering
  \caption{Compile rules in ES10}
  \label{table:rules}
\vspace*{-1em}
  \[
    \begin{array}{c?r|r|r|r|r|r|r}
      \text{Name}
      & \multicolumn{1}{c|}{\code{Stmt}}
      & \multicolumn{1}{c|}{\code{Expr}}
      & \multicolumn{1}{c|}{\code{Cond}}
      & \multicolumn{1}{c|}{\code{Value}}
      & \multicolumn{1}{c|}{\code{Ty}}
      & \multicolumn{1}{c|}{\code{Ref}}
      & \multicolumn{1}{c}{\code{SecNo}}\\\hline
      \text{\# Rules}
      & 17
      & 16
      & 8
      & 11
      & 33
      & 7
      & 21
    \end{array}
  \]
\vspace*{-2em}
\end{table}

As we discussed in Section~\ref{sec:compiler}, \textsf{Algorithm Compiler}
requires compile rules to compile given abstract algorithms to \( \ires \)
functions.  In order to cover the entire ES10,
we defined compile rules for only seven kinds as summarized in
Table~\ref{table:rules}.  The compile rule for statements, \( \code{Stmt} \),
contains 17 compile rules and generates \( \ires \) instructions.
The \( \code{Expr} \), \( \code{Cond} \), and \( \code{Value} \) compile
rules denote expressions, conditions, and values, respectively.  While
all of them generate \( \ires \) expressions, they represent different
contexts in ECMAScript.  For example,
\( \code{Expr} \) represents a context where any expression can appear,
\( \code{Cond} \) denotes a context where any boolean-valued expression
can appear, and \( \code{Value} \) represents a context where a fully
evaluated value can appear.  The \( \code{Ty} \) compile rule denotes
type names and generates string primitives in \( \ires \).  The \( \code{Ref} \)
represents references such as identifier lookup and member accesses of
map-like structures.  It generates \( \ires \) reference expressions.
Finally, the \( \code{SecNo} \) compile rule denotes section numbers
like \( \code{9.5.12} \), and it converts such numbers to
corresponding name strings like \( \code{"ProxyExoticObject.Call"} \).
% \begin{lstlisting}[style=myScalastyle]
% lazy val SecNo =
%   "9.5.12" ^^ { case x => "ProxyExoticObject.Call" } |||
%   ...
% \end{lstlisting}

\subsection{Global Setting}
We manually implemented \textsf{Global Setting} for ES10,
which has two parts: ECMAScript data types and built-in objects.

\vspace*{-.5em}
\paragraph{ECMAScript Data Types}
In ES10, Section 6 \textsf{ECMAScript Data Types and Values}
describes data types used in the specification.  It describes not only
data types explicitly exposed for JavaScript evaluation, but also all
the internal data types used in the specification.  For example, the
Environment Records are record types from identifiers to bindings for
values.  They are not explicitly accessible in JavaScript programs
but defined and used internally in the specification.

Each ECMAScript data type has several fields to store their relevant values.
We should implement such structures in order to correctly evaluate JavaScript
programs, but fields of ECMAScript data types could be abstract algorithms.
We call them \textit{method-like abstract algorithms} because they
implicitly get their receiver objects as arguments at callsites.
To mimic such implicit behavior, we added a special variable
\( \code{this} \) as the first parameter of a method-like abstract algorithm,
and passed a receiver object at its callsite by modifying
\textsf{Algorithm Compiler}.  For example, an Environment Record has
the \textsf{DeleteBinding (N)} abstract algorithm as one of its fields.
Then, it gets two parameters, the special parameter \( \code{this} \)
and normal one \( \code{N} \).  Thus, the following algorithm step:
\begin{center}
  \includegraphics[width=0.2\textwidth]{img/method-like-example.png}
\end{center}
is compiled into the following \( \ires \) instruction:
\begin{lstlisting}[style=ires]
return DclRec.DeleteBinding(DclRec, N)
\end{lstlisting}

### 2020-04-01 ase20/parser.tex
[ASE] Revised about the word: ECMAScript

\section{Parser Generator}\label{sec:parser}
In this section, we explain how to automatically generate JavaScript
parsers from a given ECMAScript specification.

\subsection{\( \bnfes \): Grammar for ECMAScript}
The ECMAScript specification describes the JavaScript syntax using an
extension of the BNF notation.  We formally define the notation and
dub it \( \bnfes \).  It consists of a number of \textit{productions}
with the following form:
\[
  \NT{A}(\param_1, \cdots, \param_k) ::=
  (\cond_1 \Rightarrow)^? \rhs_1 \mid
  \cdots \mid
  (\cond_n \Rightarrow)^? \rhs_n
\]
The left-hand side of $::=$ represents a parametric non-terminal \( \NT{A} \)
with multiple boolean parameters \( \param_1, \cdots, \param_k \).
If a non-terminal takes no parameter, parentheses are omitted for brevity.
A production has multiple alternatives separated by $\mid$ with optional conditions.
A condition \( \cond \) is either a boolean parameter \( \param \)
or its negation \( ! \param \).  An alternative \( \rhs \) is a sequence
of symbols, where a symbol \( \symb \) is one of the following:
\begin{itemize}[leftmargin=0.5cm]
\item \( \epsilon \): the empty sequence, which passes without any conditions
\item \( \T{a} \): a terminal, which is any token
\item \( \NT{A}(\argument_1, \cdots, \argument_k) \): a non-terminal,
which takes multiple arguments where each argument \( \argument_i \) is
either a boolean value \( \kwt \) or \( \kwf \), or a parameter \( \param_i \)
\item \( \symb? \): option, which is the same with \( \symb \mid \epsilon \)
\item \( +\symb \) (\( -\symb \)) : positive (negative) lookahead,
which checks whether \( \symb \) succeeds (fails) and
\textit{never consumes any input}
\item \( \symb \butnot \symb' \): exclusion, which
first checks whether \( \symb \) succeeds
and then checks whether the parsing result does not correspond to \( \symb' \)
\item \( \nolt \): no line-terminator, which is a special symbol
that restricts the white spaces between two different symbols
\end{itemize}
For example, consider the following production:
\[
  \NT{A}(\param) ::= \param \Rightarrow \T{a}
  \mid \; !\param \Rightarrow \T{b}
  \mid  \T{c}
\]
Then, \( \NT{A}(\kwt) \) means \( \T{a} \mid \T{c} \)
and \( \NT{A}(\kwf) \) means \( \T{b} \mid \T{c} \).

@@

We support the automatic semicolon insertion algorithm, which
is the most distinctive parsing feature in ECMAScript.  We extended
our parser implementation to keep track of the right-most position
that fails to be parsed in a given input.  In ECMAScript, the token at that
position is defined as an \textit{offending token} and the automatic
semicolon insertion algorithm is defined with such tokens.  The
algorithm is simple when we already have the positions of offending
tokens.  Thus, we just manually supported them by following the rules
in ECMAScript 2020.  In addition, the rules rarely change; since
ECMAScript 5.1 written in 2011, only one sub-rule was added.

@@

The second issue is that recursive descent parsers do not support left
recursion in grammars.  If a grammar has a left recursion, its parser
falls into an infinite loop.  To resolve this problem, Warth et
al~\cite{packrat-lr} proposed a mechanism to support not only direct
left recursion but also indirect one in Packrat parsing.  While we can
adopt the mechanism, we found that the ECMAScript 2020 syntax does not
use indirect left recursion.  Thus, we decided to just remove direct
left recursion by defining sub productions.

>>>>

\section{Parser Generator}\label{sec:parser}
In this section, we explain how to automatically generate JavaScript
parsers from a given ECMAScript.

\subsection{\( \bnfes \): Grammar for ECMAScript}
ECMAScript describes the JavaScript syntax using an
extension of the BNF notation.  We formally define the notation and
dub it \( \bnfes \).  It consists of a number of \textit{productions}
with the following form:
\[
  \NT{A}(\param_1, \cdots, \param_k) ::=
  (\cond_1 \Rightarrow)^? \rhs_1 \mid
  \cdots \mid
  (\cond_n \Rightarrow)^? \rhs_n
\]
The left-hand side of $::=$ represents a parametric non-terminal \( \NT{A} \)
with multiple boolean parameters \( \param_1, \cdots, \param_k \).
If a non-terminal takes no parameter, parentheses are omitted for brevity.
A production has multiple alternatives separated by $\mid$ with optional conditions.
A condition \( \cond \) is either a boolean parameter \( \param \)
or its negation \( ! \param \).  An alternative \( \rhs \) is a sequence
of symbols, where a symbol \( \symb \) is one of the following:
\begin{itemize}[leftmargin=0.5cm]
\item \( \epsilon \): the empty sequence, which passes without any conditions
\item \( \T{a} \): a terminal, which is any token
\item \( \NT{A}(\argument_1, \cdots, \argument_k) \): a non-terminal,
which takes multiple arguments where each argument \( \argument_i \) is
either a boolean value \( \kwt \) or \( \kwf \), or a parameter \( \param_i \)
\item \( \symb? \): option, which is the same with \( \symb \mid \epsilon \)
\item \( +\symb \) (\( -\symb \)) : positive (negative) lookahead,
which checks whether \( \symb \) succeeds (fails) and
\textit{never consumes any input}
\item \( \symb \butnot \symb' \): exclusion, which
first checks whether \( \symb \) succeeds
and then checks whether the parsing result does not correspond to \( \symb' \)
\item \( \nolt \): no line-terminator, which is a special symbol
that restricts the white spaces between two different symbols
\end{itemize}
For example, consider the following production:
\[
  \NT{A}(\param) ::= \param \Rightarrow \T{a}
  \mid \; !\param \Rightarrow \T{b}
  \mid  \T{c}
\]
Then, \( \NT{A}(\kwt) \) means \( \T{a} \mid \T{c} \)
and \( \NT{A}(\kwf) \) means \( \T{b} \mid \T{c} \).

@@

We support the automatic semicolon insertion algorithm, which
is the most distinctive parsing feature in ECMAScript.  We extended
our parser implementation to keep track of the right-most position
that fails to be parsed in a given input.  In ECMAScript, the token at that
position is defined as an \textit{offending token} and the automatic
semicolon insertion algorithm is defined with such tokens.  The
algorithm is simple when we already have the positions of offending
tokens.  Thus, we just manually supported them by following the rules
in ES10.  In addition, the rules rarely change; since
ES5.1 written in 2011, only one sub-rule was added.

@@

The second issue is that recursive descent parsers do not support left
recursion in grammars.  If a grammar has a left recursion, its parser
falls into an infinite loop.  To resolve this problem, Warth et
al~\cite{packrat-lr} proposed a mechanism to support not only direct
left recursion but also indirect one in Packrat parsing.  While we can
adopt the mechanism, we found that the ES10 syntax does not
use indirect left recursion.  Thus, we decided to just remove direct
left recursion by defining sub productions.

### 2020-04-01 ase20/related.tex
[ASE] Revised about the word: ECMAScript

Several approaches have defined the formal semantics of JavaScript.
\citet{lambdajs} defined a core calculus of JavaScript, and expressed the
rest as desugaring.  While it presents the core JavaScript semantics in
an extension of the $\lambda$ calculus, it does not show the semantics
correspondence defined in the ECMAScript specification.  KJS~\cite{kjs} and
JaVerT~\cite{javert} defined formal semantics of JavaScript by manually converting
the ECMAScript specification to their own formal languages.  KJS mapped
ECMAScript 5.1 in the K framework~\cite{kframework}, which can be used
for program verification and analysis.  Similarly, JaVerT converts the
specification to their own IR called JSIL to make further analysis.
Our approach provides a mechanized framework to synthesize syntactic parsers and
to automatically extract semantics
using a rule-based compilation technique, which significantly reduces human
efforts.

>>>>

Several approaches have defined the formal semantics of JavaScript.
\citet{lambdajs} defined a core calculus of JavaScript, and expressed the
rest as desugaring.  While it presents the core JavaScript semantics in
an extension of the $\lambda$ calculus, it does not show the semantics
correspondence defined in ECMAScript.  KJS~\cite{kjs} and
JaVerT~\cite{javert} defined formal semantics of JavaScript by manually converting
ECMAScript to their own formal languages.  KJS mapped
ES5.1 in the K framework~\cite{kframework}, which can be used
for program verification and analysis.  Similarly, JaVerT converts the
specification to their own IR called JSIL to make further analysis.
Our approach provides a mechanized framework to synthesize syntactic parsers and
to automatically extract semantics
using a rule-based compilation technique, which significantly reduces human
efforts.
